---
title: "Untitled"
author: "Nesij Ozdes"
date: '2023-02-23'
output: html_document
---

```{r}
library(tidyverse)
install.packages("tidyverse")
install.packages("ggplot2")
```

```{r}
getwd()
apple<-read.csv("apple_income_statement.csv")
View(apple)



```


#Summary of Data
```{r}
summary(apple)

```

#First 5 Row of Data
```{r}
head(apple,n = 5)
```

#Max and Min 
```{r}
max(apple$Total.Debt)
min(apple$Total.Debt) 



max(apple$Cash.and.Short.Term.Investments)
min(apple$Cash.and.Short.Term.Investments) 
```

#Mean and Median of Total Current Assets
```{r}
mean(apple$Total.Current.Assets)
median(apple$Total.Current.Assets)
```

#Variance and Standart Deviation of Total Current Assets
```{r}
var(apple$Total.Current.Assets)
sd(apple$Total.Current.Assets)

```

#Quantile of Total Current Assets
```{r}
quantile(apple$Total.Current.Assets)
quantile(apple$Total.Current.Assets, probs = c(0, 0.2, 0.4, 0.6, 0.8, 1))
```

#Finding Outliers
```{r}
iqr <- quantile(apple$Total.Inventory, 0.75) - quantile(apple$Total.Inventory, 0.25)
lower_total <- quantile(apple$Total.Inventory, 0.25) - 1.5 * iqr
upper_total <- quantile(apple$Total.Inventory, 0.75) + 1.5 * iqr

apple%>% filter(Total.Inventory < lower_total | Total.Inventory > upper_total)%>%

```

#Boxplot
```{r}
library(ggplot2)
quantile(apple$Total.Current.Assets)
ggplot(apple, aes(y =Total.Current.Assets)) + 
  geom_boxplot()

quantile(apple$Total.Current.Assets, probs = c(0, 0.2, 0.4, 0.6, 0.8, 1))

```


#Visualization of Total Inventory
```{r}
boxplot(apple$Total.Inventory,
        col="#33ffad",
        main="Boxplot")

hist(apple$Total.Inventory,
     col="#33ffad",
     main="Histogram",
     xlab="Total Inventory",
     ylab="Frequency",
     labels=TRUE)

```


#Visualization of Cash and Short Term Investments
```{r}
hist(apple$Cash.and.Short.Term.Investments,
     col="#ff66b3",
     main="Histogram for Cash and Short Term Investments",
     xlab="Cash and Short Term Investments",
     ylab="Frequency",
     labels=TRUE)

boxplot(apple$Cash.and.Short.Term.Investments,
        col="#ff0066",
        main="Boxplot")

```

#Visualization of Total Debt
```{r}
hist(apple$Total.Debt,
     col="#3385ff",
     main="Histogram for Total Debt",
     xlab="Total Debt",
     ylab="Frequency",
     labels=TRUE)

boxplot(apple$Total.Debt,
        col="#3385ff",
        main="Boxplot")

```

#What Percent of Apple's Total Debt is less than 35000?
```{r}
mean(apple$Total.Debt)
sd(apple$Total.Debt)

pnorm(35000, mean = 37601.4, sd = 1449.216 )


```

#What Total Debt is 90% less than Apple's?
```{r}
qnorm(0.9, mean = 37601.4, sd = 1449.216 )


```

#What Percent of Apple's Total Inventory is less than 11000?
```{r}
mean(apple$Total.Inventory)
sd(apple$Total.Inventory)

pnorm(11000, mean = 11694.4, sd = 2055.748 )

```

#What Total Inventory is 50% less than Apple's?
```{r}
qnorm(0.5, mean = 11694.4, sd = 2055.748 )
```

#What Percent of Apple's Cash and Short Term Investments is less than 6500?
```{r}
mean(apple$Cash.and.Short.Term.Investments)
sd(apple$Cash.and.Short.Term.Investments)

pnorm(6500, mean = 7559.2, sd = 1287.064 )

```

#What Cash and Short Term Investments is 40% less than Apple's?
```{r}
qnorm(0.4, mean = 7559.2, sd = 1287.064 )
```

